{\plant}: A package for modelling forest trait ecology \& evolution

### 2016-01-18 ms.tex
Add section on data (and code) accessibility (as requested)
They ask for data, but i decided to add link to github repository
reproducing paper as well
Rename strategy object from FFDev to FF16r
    - triggered by final submission of paper to MEE
    - better to have date in alternative strategy name
    - reflects changes made in traitecoevo/plant/0fe3ada1d85720821ec9a096d309295cf04ef176

While we have implemented a particular physiological model
(\texttt{FF16}), the package is designed to allow arbitrary
additional physiologies to be introduced. Users are able to modify the
physiological model in three different ways. First, one can vary the
parameters of the \texttt{FF16} model directly (see Appendix
\ref{sec:FF16} for the list of parameters and Appendix \ref{sec:code} for code
examples). Second, we allow for changes in key parameters to bring
about changes in other parameters (a hyper-parameterisation), enabling the
straightforward modelling of trade-offs. For example, the
trait \textsc{lma} (leaf mass per unit leaf area) is used by default to estimate
the rate of leaf turnover ($k_{\rm l}$), based on an observed scaling
relationship spanning across diverse vegetation and plant functional
types \citep{Wright-2004},
$$k_{\rm l} = \beta_{{\rm kl}1} \, \left(\phi / \phi_0\right)^{-\beta_{{\rm kl}2}},$$
where $k_{\rm l}$ and $\phi$ (\textsc{lma}) are both parameters of the core physiological
model, and $\beta_{{\rm kl}1}, \beta_{{\rm kl}2}, \phi_0$ are hyper-parameters. Such
linkages are defined within a user-supplied hyper-parameterisation function
(see Appendix \ref{sec:FF16} for details, or Appendix
\ref{sec:code} for code examples).
%
Finally, rather than varying the parameters of the existing equations
in the \texttt{FF16} model, the equations themselves can be
fundamentally changed. This requires defining a new physiological
model in a new C++ file and compiling that into the package. As an
example, in the \texttt{FFdev} physiology, we have shown how to modify the
function determining allocation to reproduction.

@@

>>>>

While we have implemented a particular physiological model
(\texttt{FF16}), the package is designed to allow arbitrary
additional physiologies to be introduced. Users are able to modify the
physiological model in three different ways. First, one can vary the
parameters of the \texttt{FF16} model directly (see Appendix
\ref{sec:FF16} for the list of parameters and Appendix \ref{sec:code} for code
examples). Second, we allow for changes in key parameters to bring
about changes in other parameters (a hyper-parameterisation), enabling the
straightforward modelling of trade-offs. For example, the
trait \textsc{lma} (leaf mass per unit leaf area) is used by default to estimate
the rate of leaf turnover ($k_{\rm l}$), based on an observed scaling
relationship spanning across diverse vegetation and plant functional
types \citep{Wright-2004},
$$k_{\rm l} = \beta_{{\rm kl}1} \, \left(\phi / \phi_0\right)^{-\beta_{{\rm kl}2}},$$
where $k_{\rm l}$ and $\phi$ (\textsc{lma}) are both parameters of the core physiological
model, and $\beta_{{\rm kl}1}, \beta_{{\rm kl}2}, \phi_0$ are hyper-parameters. Such
linkages are defined within a user-supplied hyper-parameterisation function
(see Appendix \ref{sec:FF16} for details, or Appendix
\ref{sec:code} for code examples).
%
Finally, rather than varying the parameters of the existing equations
in the \texttt{FF16} model, the equations themselves can be
fundamentally changed. This requires defining a new physiological
model in a new C++ file and compiling that into the package. As an
example, in the \texttt{FF16R} physiology, we have shown how to modify the
function determining allocation to reproduction.

@@

\section{Data Accessibility and Reproducibility}

Source code for reproducing the entire contents of this paper is available at
\href{https://github.com/traitecoevo/plant\_paper}{github.com/traitecoevo/plant\_paper};
see also Appendix \ref{sec:code} for worked examples reproducing the figures.
This paper does use any data.
